PyPy's Approach to Virtual Machine Construction

### 2006-05-31 talk/dls2006/paper.tex
Rephrase.

  [figure 0: flow graph and annotator, e.g. part of doc/image/translation.*
             then a stack of transformations
  ]
\end{verbatim}
%
\begin{enumerate}
\item We take as input RPython functions,\footnote{The input to our
       translation chain are indeed loaded runtime function objects,
       not source code or ASTs.  This allows us to use unrestricted
       python for meta-programming purposes at load time, in a
       seemingly staged programming approach, in which the whole of
       the source program -- as Python program -- produces the RPython
       program input to the tool-chain as the object graph loaded in
       memory.  This includes both the relevant functions and prebuilt
       data.} and convert them to control flow graphs -- a structure
       amenable to analysis.  These flow graphs contain polymorphic
       operations only: in Python, almost all operations are
       dynamically overloaded by type.

>>>>

  [figure 0: flow graph and annotator, e.g. part of doc/image/translation.*
             then a stack of transformations
  ]
\end{verbatim}
%
\begin{enumerate}
\item We take as input RPython functions,\footnote{The input to our
       translation chain are indeed loaded runtime function objects,
       not source code or ASTs.  This enables a form of staged
       programming in which we can use unrestricted
       Python for meta-programming purposes at load time: the whole of
       the source program -- as Python program -- produces the RPython
       program input to the tool-chain as the object graph loaded in
       memory.  This includes both the relevant functions and prebuilt
       data.} and convert them to control flow graphs -- a structure
       amenable to analysis.  These flow graphs contain polymorphic
       operations only: in Python, almost all operations are
       dynamically overloaded by type.
